A Comparative Quality Metric for Fuzzing with Logic State Coverage

### 2024-03-05 paper/main.tex
paper: enhanced visual aid for interestingness

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{images/repr.pdf}
  \caption{Example control flow graph and the number of program behaviors
  (numbers in a grid) given two branch hit counts. $m(b)$ denotes the hit count
  of the branch $b$. Dotted lines demarcate whether the corresponding branch is
  hit or not (i.e., presence in a logic state).}
  % Each region surrounded by dotted lines constitutes one logic state.}
  \label{f:repr}
\end{figure}

@@

\autoref{f:repr} shows an example control-flow graph and the number of possible
program behaviors for each pair $(m(b_1), m(b_2))$, where $m(b)$ is the hit
count of the branch $b$. For example, there are two possible program behaviors,
$b_2$ after $b_1$ or $b_1$ after $b_2$, when $(m(b_1), m(b_2))=(1, 1)$. 
%Notice that the back edge $b_3$ is always taken $m(b_1)+m(b_2)$ times by the shape of the graph.
%
The dotted lines demarcate whether the corresponding branch is hit or not, which
also corresponds to the presence of the branch in a logic state.
%the beginning of a new power-of-2 branch hit count
%(e.g., 1, 2, 4, ...), where the hit counts between them share the same integer
%bucket. 
The surrounded region has the same set of satisfied branches, constituting
\emph{one logic state}.

As shown, the program behaviors with more repetitive branches are grouped with
more program behaviors as one logic state.  For example, a program behavior
having only one repetitive branch (either $b_1$ or $b_2$) falls into the slim
logic states adjacent to axis (bottom right and top left), while a behavior
having two repetitive branches (both $b_1$ and $b_2$) falls into the large logic
state (top right). This results in observing repetitive (i.e., less interesting)
program states represented by fewer logic states, leading to smaller logic state
coverage.

>>>>

\begin{figure}[t]
  \centering
  \vspace{-1em}
  \includegraphics[height=4.5cm]{images/repr-cfg.pdf}
  \includegraphics[height=4.5cm]{images/repr-grid.pdf}
  \vspace{-.5em}
  \caption{Example control flow graph and its logic states (colored box) that
  the program behaviors with different branch hit counts belong to. $m(b)$
  denotes the hit count of branch $b$.}
  % Each region surrounded by dotted lines constitutes one logic state.}
  \label{f:repr}
\end{figure}

@@

\autoref{f:repr} shows an example control-flow graph and its logic states
(colored boxes) that the program behaviors with different sets of satisfied
branches belong to.
%, where $m(b)$ denotes the hit count of a branch $b$. 
For example, a program behavior that does not hit any colored branches (i.e.,
$m(b_1)=m(b_2)=m(b_3)=0$) belongs to \cbox{black}, and a program
behavior that only hits one of them (e.g., $m(b_i)>1$ and $m(b_j)=0$ for $i \in
\{1,2,3\}$ and $j \ne i$) belongs to the logic state of the corresponding color
(\cbox{red}, \cbox{green}, and \cbox{blue}).
%The dotted lines demarcate whether the corresponding branch is hit or not, which
%also corresponds to the presence of the branch in a logic state.
%The surrounded region has the same set of satisfied branches, constituting
%\emph{one logic state}.

The figure shows the increasing size of logic states as their constituent
program behaviors involve more repetitive branches. For example, a program
behavior with two repetitive branches (i.e., $b_1$ and $b_2$, $b_2$ and $b_3$,
or $b_1$ and $b_3$) falls into a larger logic state (e.g., \cbox{yellow},
\cbox{cyan}, and \cbox{magenta}), and a behavior with three repetitive branches
(i.e., all $b_1$, $b_2$, and $b_3$) falls into the largest logic state (i.e.,
\cbox{gray}).
%
This results in observing repetitive (i.e., less interesting) program states
represented by fewer logic states, leading to smaller logic state
coverage.\footnote{It is worth noting that a coordinate in the grid does
\emph{not} represent one program behavior. For example, a coordinate (1, 1, 0)
represents two program behaviors, $b_1$ before $b_2$ and $b_2$ before $b_1$.
However, it does not affect the relative size of visualized logic states because
a coordinate only has more program behaviors as it gets further from the
origin.}
